Reproduction

### 2024-11-04 pages/reproduction.qmd
docs(reproduction): add model run times

## Scope

@@

## Time to completion

@@

>>>>

## Scope and reproduction

@@

## Time to complete reproductions

@@

## Model run times

For reference, the run times for the models are detailed below. It's worth being aware that these are not compared on a "level playing field" as they were run on different machines, and with/without parallel processing or parallel terminals.

| Study | Machine specs | Model run time | Additional details |
| --- | --- | --- | --- |
| @shoaib_simulation_2021 | Intel Core i7-12700H with 32GB RAM running Ubuntu 22.04.4 Linux | **22 minutes 26 seconds** | This is based on the combined runtime of the notebooks which use 10 replications (rather than 100) and parallel processing, but with each notebook run seperately. |
| @huang_optimizing_2019 | Intel Core i7-12700H with 32GB RAM running Ubuntu 22.04.4 Linux | **29 minutes 10 seconds** | Combined time from notebooks run seperately. |
| @lim_staff_2020 | Intel Core i7-12700H with 32GB RAM running Ubuntu 22.04.4 Linux | **49 minutes and 17 seconds** |
| @kim_modelling_2021 | Intel Core i9-13900K with 81GB RAM running Pop!_OS 22.04 Linux | **6 hours 53 minutes** |We reduced the number of patients in the simulation from 10 million to 1 million, to improve run times. Note, you can expect the runtime to be **notably longer** on machines with lower specs than this. For example, I ran surveillance scenario 0 on an Intel Core i7-12700H with 32GB RAM running Ubuntu 22.04.4 Linux. The runtime increased from **4 minutes 28 seconds** up to **21 minutes 59 seconds**. |
| @anagnostou_facs-charm_2022 | Intel Core i7-12700H with 32GB RAM running Ubuntu 22.04.4 Linux | **Only a few seconds**. |
| @johnson_cost_2021 | Intel Core i9-13900K with 81GB RAM running Pop!_OS 22.04 Linux | **At least 1 day 11 hours** | It was run from the command line via multiple terminals simultaneously - hence, the exact times are impacted by the number being ran at once. The base case scenarios were ran at the same time, and took an overall total time of **20 hours 40 minutes**.  The sensitivity analysis scenario were all ran at the same time, and took an overall total of **1 day 10 hours 57 minutes**. Four files (scenarios 2 and 3) had to be re-run seperately after fixing a mistake, and when just those were run, the total was **21 hours 26 minutes** (quicker than when they were run as part of the full set of scenarios, when they took up to 1.3 days). Based on this, if you were to run all scenarios at once in parallel in seperate terminals, you could expect a run time of **at least 1 day 11 hours**, but would be higher than that (since the more run at once, the lower it takes, as you can see from the scenario 2 and 3 times above). |
| @hernandez_optimal_2015| Intel Core i9-13900K with 81GB RAM running Pop!_OS 22.04 Linux | **9 hours 16 minutes** | This involved running the models within each experiment in parallel, but each of the experiment files seperately. If these are run at the same time (which I could do without issue), then you will be able to run them all within **4 hours 28 minutes** (the longest experiment) (or a little longer, due to slowing speeds from running at once). Also, this has excluded one of the variants for Experiment 3, which I did not run as it had a very long run time (quoted to be 27 hours in the article) and as, regardless, I had not managed to reproduce the other sub-plots in the figure for that experiment. |
| @wood_value_2021 | Intel Core i9-13900K with 81GB RAM running Pop!_OS 22.04 Linux | **48 hours 25 minutes** | It ran in a single loop, so required the computer to remain on for that time. This time includes all scenarios - but, for just the base scenario, the run time was **2 hours 3 minutes**. |
: {tbl-colwidths="[20, 20, 20, 40]"}
